Collaborative Test-Driven Scientific Model Validation

### 2013-11-23 sciunit-icse14/sciunit-icse14.tex
updated figure caption

\section{Introduction}
\begin{figure*}[t]
\centering
\includegraphics[scale=0.4]{diagram1.pdf}
\vspace{-25px}
\caption{NeuronUnit overview. NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework. 
NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the \textit{Open Source Brain Project} (OSB, \cite{gleeson_open_2012}, \url{http://www.opensourcebrain.org}), and single neuron electrophysiology data available as part of the NeuroElectro Project (Neuroelectro, \cite{tripathy_neuroelectro:_2012}, \url{http://neuroelectro.org}).  
Records of test results for various model/test combinations are accessible via SciDash, which indexes GitHub repositories of these records, models, and tests so they can be searched and filtered by the community.}  
\label{fig:sciunit_overview}
\end{figure*}

>>>>

\section{Introduction}
\begin{figure*}[t]
\centering
\includegraphics[scale=0.4]{diagram1.pdf}
\vspace{-25px}
\caption{The central table summarizes the performance of a collection of models against a suite of tests. These are collaboratively curated in \emph{suite repositories} using social coding infrastructure -- Github -- combined with a portal that organizes and summarizes them. Tests are derived from data and models are derived from scientific theories, parameterized by \emph{training data}. Tests communicate with models using interface specifications that are also collaboratively developed in repositories that build upon the core SciUnit testing framework. These repositories can also contain common test and model families and bridges to existing infrastructure and tools.}  
\label{fig:sciunit_overview}
\end{figure*}
